\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{blindtext}
\usepackage{parskip}
\usepackage[none]{hyphenat}
\usepackage[total={6in, 9in}]{geometry}
\usepackage[sorting=none]{biblatex}
\usepackage{xpatch}
\usepackage{glossaries}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage{colortbl}
\usepackage[table]{xcolor}
\setlength\bibitemsep{20pt} 

\sloppy

\newfontfamily{\codefont}{CamingoCode}


\addbibresource{References.bib}

\title{Asthma App}
\author{Manar Ajhar \\ \texttt{manarajhar@hotmail.com} \and Dr. Suha Al-Naimi \\ \texttt{sal-naimi@sharjah.ac.ae}}
   
\date{\today}

\begin{document}

\maketitle

\section*{Abstract}
[Text Here]

\section{Introduction}
[Text Here]
\include{2. Methodology and Procedures}

\section{Evaluation}
[Text Here]
\section{Conclusion and Future Work}
[Text Here]

\section{Definitions}
\begin{itemize}
    \item{Cosine: The ratio of the adjacent side of a corner in a right triangle to the hypotenuse of the triangle: $cos(\theta) = \frac{adjacent}{hypotenuse}$.}

    \item{Sine: The ratio of the opposite side of a corner in a right triangle to the hypotenuse of the triangle: $sin(\theta) = \frac{opposite}{hypotenuse}$.}
    
    \item{Raycasting: using a straight line that starts from one point and continues infinitely (by default) until it detects an object in the way.}
    
    \item{Canvas: A UI element that contains other elements, including (but not limited to) text, images, buttons, or other canvases.}

\begin{itemize}
    \item{On-Screen Canvas: A canvas that is always fixed in the display’s screen.}
    
    \item{World Space Canvas: A canvas that exist in a world or scene with other objects.}
\end{itemize}

\end{itemize}

\subsection{Types of Programming Variables}
\begin{itemize}
    \item{Enumerator: A variable type in programming that has a certain number of possible values where one is selected, for example:
    
    \begin{itemize}
    \item{Fruit:}
    	\begin{enumerate}
    	\item{Apple,}
    	\item{Orange,}
    	\item{Banana,}
    	\item{Mango,}
    	\item{Pear,}
    	\item{Strawberry,}
    	\end{enumerate}
    \item{Animal:}
        \begin{enumerate}
    	\item{Cat,}
    	\item{Dog,}
    	\item{Horse,}
    	\item{Pigeon,}
    	\item{Turtle,}
    	\end{enumerate}
    \end{itemize} 
    }   
    \item{Integer: A whole number, such as: 0, 1, 3, -8, 100, 2006.}
    
    \item{Float: A decimal number, such as: 0.0, 0.54, 1.0, 5.2, -10.33, 7604.099.}
    
    \item{String: A text or sequence of characters, such as: “Hello World, 12381 42!”.}
    
    \item{\fontspec{CamingoCode}Vector2\normalfont: A collection/array of two float variables. The first one is named ‘x’, and the second one is named ‘y’.}
    
    \item{\fontspec{CamingoCode}Vector3\normalfont: A collection/array of three float variables. In addition to the two variables in \fontspec{CamingoCode}Vector2\normalfont, the third one is named ‘z’.}
    
    \item{Boolean: A variable type that only has two possible values: ‘\fontspec{CamingoCode}true\normalfont’ or ‘\fontspec{CamingoCode}false\normalfont’.}
    \item{List: A dynamic collection/array of values or data of the same variable type. Examples of variable types include (but not limited to) integers, floats, strings, classes and their sub-classes, objects, or other lists.}
    
        \item{Dictionary: A special list that contains data as key-value pairs. The key:
        
        \begin{enumerate}
        
        \item{\textbf{MUST} be unique}
        \item{Is associated with a value}
        \item{\textbf{MUST} be a simple value type (typically an integer or a string)}
        \item{Is a quicker way to index values, even in unordered data \cite{DictionaryMeaning}.}        
        \end{enumerate}        
        }    
    \item{Interface (three meanings):
    \begin{enumerate}
    \item{A way information is shown in a computer or device to its user. Example of interfaces in this document's topic are the canvases and the elements they contain and the way they are structured and presented \cite{InterfaceMeaning}. Other examples of interfaces include the green arrows and texts in the assembly game that tell they user what to do, and the unique canvas design in the MCQ game.}
    
    \item{The way that a user is able to interact with a program. For example, the buttons, sliders, and input fields that are shown in the canvases \cite{InterfaceMeaning}.}
    
    \item{A programming structure that enforces certain properties on an object or class. For example, there can be a phone class, a computer class, and a TV class. All of these classes \textbf{MUST HAVE} a ``\fontspec{CamingoCode}TurnOn()\normalfont'' function, but how the function is written in each specific class is up to the programmer \cite{ProgInterfaceMeaning}.}
    
    \end{enumerate}
    
    }
    
 \end{itemize}
\section{Acronyms}

\begin{itemize}
    \item{Enum: Enumerator}
    
    \item{AR: Augmented Reality}
    
    \item{UI: User Interface}
\end{itemize}

\printbibliography

\end{document}